---
title: "GVL_session1"
author: "Myfanwy Johnston"
date: "8/19/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(artemis)
options(digits = 3)

d = eDNA_data # built-in dataset - fine for simple examples.

# Cq = ln[eDNA]*std_beta + std_alpha
# ln[eDNA] = (Cq - std_alpha)/std_beta

```

# Intercept-only model

Essentially a model of the average value of ln[eDNA]. ln(eDNA)_sigma = the standard deviation.  Normal distribution (-10.2, 3.67).

```{r}
m0 = eDNA_lm(Cq ~ 1, # conventional lm/lme4 notation for an intercept-only model.
             data = d,
             std_curve_alpha = eDNA_data$StdCrvAlpha_lnForm[1],
             std_curve_beta = eDNA_data$StdCrvBeta_lnForm[1],
             seed = 20)

summary(m0)
```

The estimate here represents the baseline ln[eDNA] in this data set, averaged across all predictor values in the data, is -10.20.  We can see what this concentration corresponds to in Cq using the standard curve formula and the convenience function:

```{r}
# Cq = (ln[eDNA]*std_beta) + std_alpha

(-10.2*d$StdCrvBeta_lnForm[1]) + d$StdCrvAlpha_lnForm[1]

```


# Single predictor models & interpretation

Once you add a predictor, the intercept is the ln[eDNA] when all other predictors are set to 0.  In practice this value may not be meaningful (you can't have a 0 volume sample, for example).

The other estimates (coefficients) are the offset from the intercept.  

```{r m1}

d$lnconc = (d$Cq - d$StdCrvAlpha_lnForm)/d$StdCrvBeta_lnForm
mean(d$lnconc)
sd(d$lnconc)

plot(lnconc ~ Distance_m, d)

m1 = eDNA_lm(Cq ~ Distance_m,
             data = d,
             std_curve_alpha = eDNA_data$StdCrvAlpha_lnForm,
             std_curve_beta = eDNA_data$StdCrvBeta_lnForm,
             seed = 20)

summary(m1)

chk = loo(m1)

plot(chk)


preds = predict(m1) # list; one row for each data point, 4000 posterior samples

# plot those predictions against obs

```

Checks: are the estimates sane?  Plot observed vs. predicted; look for systematic weirdness.  Make a new model, compare it with the first one (loo or WAIC).

Residuals roughly correspond to posterior predictive checks.  Frequentist: you get point predictions, and residuals = observed - predicted. QQ plots wouldn't be right - 

Posterior checks for artemis models: you're looking for values that are not being predicted well, and whether those are systematic. LOO and WAIC do much the same thing.  Can plot observed vs. predicted.

```{r}

d2 = readRDS("~/NonDropboxRepos/wrangle_elaphos/data_clean/.rds")
table(d2$Experiment)

m2 = eDNA_lm(Cq ~ Distance_m + Volume_mL,
             data = d,
             std_curve_alpha = eDNA_data$StdCrvAlpha_lnForm,
             std_curve_beta = eDNA_data$StdCrvBeta_lnForm,
             seed = 20)

summary(m2)

```

Interaction is saying we think that the effect of volume changes with distance, or the effect of distance changes with volume.  A better set might be distance and species (because maybe different shedding rates).  Continuous x Continuous is harder to interpret/use than continuous x categorical.

