---
title: "GVL_session1_template"
author: "Myfanwy Johnston"
date: "8/19/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(artemis)
source("R/utils.R")
options(digits = 3)

d = eDNA_data # built-in dataset - fine for simple examples.
```

## Exploratory data analysis

```{r}

head(d)
tail(d)
str(d)

table(d$TechRep)
table(d$Distance_m, d$Volume_mL)
colSums(is.na(d))
rowSums(is.na(d))

ggplot(d, aes(x = Distance_m, y = Cq)) +
  geom_jitter(width = 0.3, size = 1) +
  geom_smooth(method = "lm")

lm1 = lm(Cq ~ 1, data = d)
summary(lm1)

```



## Intercept-only model

Make an intercept-only model of Cq from the built in data set we've copied above.  Call it m0. What do the estimates in `summary(m0)` mean?  

```{r m0}

m0 = eDNA_lm(Cq ~ 1,
             data = d,
             std_curve_alpha = d$StdCrvAlpha_lnForm,
             std_curve_beta = d$StdCrvBeta_lnForm)


```

## Including a predictor

Now let's model Cq ~ Distance_m.  What does the intercept estimate mean here? The other fixed effects estimates?  How should we interpret their signs and Credible Intervals?

```{r m1}

m1 = eDNA_lm(Cq ~ Distance_m,
             data = d,
             std_curve_alpha = d$StdCrvAlpha_lnForm,
             std_curve_beta = d$StdCrvBeta_lnForm)

summary(m1)

```

## Including two predictors

What changes when you have multiple predictors?

```{r m2}

m2 = eDNA_lm(Cq ~ scale(Distance_m) + scale(Volume_mL),
             data = d,
             std_curve_alpha = d$StdCrvAlpha_lnForm,
             std_curve_beta = d$StdCrvBeta_lnForm,
             seed = 20)

summary(m2)

```



## Including two predictors and multiple standard curves

```{r m4}



```


## Including random effects


